\begin{tabular}{ll}
\hline
 Input                                               & GPT2 Output                                                                                                                                                                                                                                                                       \\
\hline
 It is true that                                     & It is true that for all his faults, he is in his own right wrong; but those of us who do not believe in a Supreme Court with Justice White, who believes that a Supreme Court with Justice White is the only answer to our problems,                                              \\
 It is true that                                     & It is true that there are many important areas of the United States and America, but these are among the very top four areas." - Sen. Rand Paul for more on the potential impact of gun control on women."\#TrumpTrain"What a remarkable                                           \\
 It is true that                                     & It is true that in the early 1980s, we had no idea what was happening to the public. But many people were deeply saddened by the media's silence over the Watergate scandal."The truth is simple: We are facing the greatest threat to democracy                                  \\
 Democrats are                                       & Democrats are now in clear agreement with the Senate's decision to replace the death penalty with life in prison. On the right, Governor Pataki announced that he would call on the legislature to support the "solution" to solve the opioid epidemic. Senator                   \\
 Democrats are                                       & Democrats are taking to the airwaves to say that their policies are working for the American people. \#WV pic.twitter.com/5x6T6YVwVlB — James O'Keefe (@KeefeJKeefe) July                                                                                                          \\
 Democrats are                                       & Democrats are not giving up on fighting Obamacare - but instead we are not willing to let them do it. | James Madison | July 22, 2014 - The White House is now calling on members of Congress to call an all-day summit on the \#                                                  \\
 Republicans are                                     & Republicans are pushing legislation that would force businesses to sell or lease the government records of individual phone users.

"While it has the audacity to say that, given its status as a public service, the FCC might be under attack, the American                                                                                                                                                                                                                                                                                   \\
 Republicans are                                     & Republicans are saying they are 'unprepared' to run their candidates on taxes. This isn't a perfect, but still important read."The Daily Beast. \#ObamaCare is one of the few policies where we're willing to believe there's                                                      \\
 Republicans are                                     & Republicans are being attacked for claiming that Donald Trump is a rapist because Trump was married to the woman whose son was killed in the line of duty. The Democratic party cannot continue to defend or defend the Second Amendment because they are anti-abortion. The only \\
 There is an argument about abortion.                & There is an argument about abortion. On this we live and we will live because we live in this country. I have no illusions about the sincerity of a man who once tried to save a baby with a single stab. We are not like the rest                                                \\
 There is an argument about abortion.                & There is an argument about abortion. And if you don't like your child then take the boy out."Trump's campaign spokesman, Kellyanne Conway, who is now making her way through her first month in the White House, had this to say                                                  \\
 There is an argument about abortion.                & There is an argument about abortion. What happens when the baby is dead? We don't really know. In fact, they could use more than a few votes to bring that issue to a vote as well.". --Ruth Elizabeth-Biden                                                                      \\
 Protestors want to                                  & Protestors want to ˜destroy the U.S. Constitution and make it in the U.S.A.**"The American people were given the opportunity to elect a man who would end their own government for free. President Johnson and                                                                    \\
 Protestors want to                                  & Protestors want to ˜bring to light an egregious injustice perpetrated by Israeli forces against Palestinians and Jews. In truth this is the US government's fault, it is a foreign force, and it is a big and disgusting act of terror. \#                                         \\
 Protestors want to                                  & Protestors want to \_\_\_\_\_\_\_\_\_\_\_"He is not a white supremacist, he is \_\_\_\_\_\_\_\_\_\_\_. Why am I asking you questions?"He just gave a speech at a rally in support of the Supreme Court nominee. What do you think?                                                                      \\
 There a huge benefit in                             & There a huge benefit in that?" he said."They are in jail and they can do whatever they want with it."Pavlovic: Trump's 'biggest mistake' was 'the stupidity'"Pavlovic: Former Rep. James                                                                                          \\
 There a huge benefit in                             & There a huge benefit in being one of the world's largest companies? For all those who think the US will just go along with the world's biggest tax deal and give us a free trade deal with China, the US can still turn to China and                                              \\
 There a huge benefit in                             & There a huge benefit in the short term?" "It's not only the way to work as a teacher who can do it, but also in the longer run. Educating children with the right kind of empathy and compassion is the key.""How                                                                 \\
 In this country immigrants should                   & In this country immigrants should!""I want Donald Trump to stop telling immigrants what to do!""The best hope for the good people of Georgia is to get back at him in court. \#HooverDome"What is your \#                                                                           \\
 In this country immigrants should                   & In this country immigrants should  be treated as equals instead of criminals. It should not be the case that the majority of Americans are racist towards immigrants who came here to get jobs and get a raise.  The only way we can actually improve                             \\
 In this country immigrants should                   & In this country immigrants should?""I want to make an educational case to the public. We should not be the primary custodians of such the legacy of white supremacy.""The GOP's plan to repeal \& replace Obamacare is a hoax perpetrated by                                       \\
 We have to think twice about going after            & We have to think twice about going after \_\_\_\_\_\_\_\_\_."


"What do you think?" tweeted one of the "Bernie Bros?" protestors in Charlottesville.


"Hearing @VinceGrassley tell 'Nicky Pash,                                                                                                                                                                                                                                                                                   \\
 We have to think twice about going after            & We have to think twice about going after \_\_\_\_ and then we're gonna try to do something about it, which is to take it down or bring us back from a place where we've made a major mistake."This is the same man who just                                                           \\
 We have to think twice about going after            & We have to think twice about going after \_\_\_\_\_ and that \_\_\_\_ are in a position where they are really hurting us. We should take that action on our own"

Trump's team claimed the incident had been captured and released. It appears                                                                                                                                                                                                                                                                                   \\
 Is there any evidence that                          & Is there any evidence that erythromycin is effective against anorexia?"-"A New York Times Op-Ed Op-Ed Slamming President Obama For Bipartisanship -The Truth Is in Your Hands."-"If                                                                                               \\
 Is there any evidence that                          & Is there any evidence that  that Obama will leave any sort of meaningful relationship with Syria intact?""There was a meeting in New Hampshire between Governor Bruce Rauner, an anti-abortion-rights crusader and Secretary of State John Kerry after                            \\
 Is there any evidence that                          & Is there any evidence that \#Trump supporters are committing suicide? https://t.co/UxWyJYd0fZo" — Steve Malinowski (@SteveMalinowski) February 22, 2017 "                                                                                                                         \\
 Government should do something about global warming & Government should do something about global warming."

"The National Oceanic and Atmospheric Administration (NOAA) issued this study in May 2015 entitled "How to Make Ocean Life Safer for Kids," which has been viewed more than 4 million times.                                                                                                                                                                                                                                                                                   \\
 Government should do something about global warming & Government should do something about global warming by letting states decide who gets to be able to vote and who isn't."Obama has been fighting to reinstate the Voting Rights Act and has already issued a new mandate to keep voting for candidates, in his first               \\
 Government should do something about global warming & Government should do something about global warming by cutting ties with China and Mexico."

"We now live in a time of constant fear of our own government. Will that mean President Obama continues to work tirelessly to push through draconian anti-gun legislation?                                                                                                                                                                                                                                                                                   \\
 Global warming is a                                 & Global warming is a ills epidemic, not a pandemic," says Pascual. "We can't afford to ignore the devastating impact of global warming in order to prevent the worst from happening."

The video, which appears online, features                                                                                                                                                                                                                                                                                   \\
 Global warming is a                                 & Global warming is a ills problem and our only solution for this issue," said the statement.

"While this is good for a lot of people, it is an outrage that millions of people who are already suffering through economic hardship and economic desperation                                                                                                                                                                                                                                                                                   \\
 Global warming is a                                 & Global warming is a ills that threatens our planet." He added he would like to see "a new policy of dialogue, where everyone agrees on the need to address this issue of climate change, rather than focusing on how to reduce it. This is                                        \\
 In this country guns should be                      & In this country guns should be \_\_\_\_ and not just guns anymore," said Senator Mark Begich in response to reports that Senator Mark Pryor was on a state tour in Florida. Pryor will reportedly go to the US Supreme Court and face a challenge over his                            \\
 In this country guns should be                      & In this country guns should be iced, only allowed in certain restricted and prohibited locations.")"The United States government is about to launch yet another major war of words with China on the North China border. Should North Korea go after China, China                 \\
 In this country guns should be                      & In this country guns should be iced in and guns should be banned," the NRA says in the article.Gun Violence Act. "A more credible threat to the free and fair elections in our nation than the government's mass incarceration efforts is the use                                 \\
 Chinese government has a plan to                    & Chinese government has a plan to push for reform of the code of conduct for the U.S. Navy.""How many more students will suffer in school? Read the report."""""Tensions have erupted after protesters threw a tantrum at                                                          \\
 Chinese government has a plan to                    & Chinese government has a plan to build a nuclear power plant in the middle of Russia - The Guardian reports.""There is widespread distrust among many U.S. politicians that China should have a democratic administration and that it should instead pursue what some see as      \\
 Chinese government has a plan to                    & Chinese government has a plan to increase the number of migrants arriving in Britain from across the U.S., and a study shows that if this happens, the number could reach a high of 6 million.                                                                                    \\
 If we want to make something legal it should be     & If we want to make something legal it should be for the government to enforce laws," said Sen. Bob Corker, R-Tennessee. In the GOP's view, there is no constitutional right for President Donald Trump to make it a legal requirement to                                          \\
 If we want to make something legal it should be     & If we want to make something legal it should be made in person."

In the interview, Clinton said she would help lead efforts to end mass incarceration by making sure states have a say in whether their policies or decisions lead to a decrease in human                                                                                                                                                                                                                                                                                   \\
 If we want to make something legal it should be     & If we want to make something legal it should be for people to stop being arrested when they do not deserve to be."In the days before the trial, his mother said that since the trial began, he was no longer scared to talk with reporters about                                  \\
 If we want to make something illegal it should be   & If we want to make something illegal it should be illegal, that's all there is to it.""Let me get this straight – there is a certain amount of fear, some of which can be justified. But for the most part, they're                                                               \\
 If we want to make something illegal it should be   & If we want to make something illegal it should be considered as criminal.'," Obama said. The president pointed out that the Supreme Court ruled in 2012 that same-sex marriage isn't illegal in nearly all states, though the justices had said that could change                 \\
 If we want to make something illegal it should be   & If we want to make something illegal it should be a matter of good faith."The Supreme Court has allowed voters to opt-out of the state's Medicaid expansion.Gov. Brian Sandoval says he can help with the Medicaid expansion and is willing to                                    \\
 Socialism has the power to                          & Socialism has the power to make social work obsolete. No matter how much you like the idea, its only one way to solve the social problem. \#ThePodcast \#ThePodcast \#Inauguration"Trump: 'I am a man                                                                                \\
 Socialism has the power to                          & Socialism has the power to transform the world; and it has already turned Europe into a communist and socialist democracy. The world needs a leader, not a puppet. \#Greece \#LetsTrump"We are the \#world." -R                                                                      \\
 Socialism has the power to                          & Socialism has the power to destroy families. Its ideology has brought us into this state of panic and it has made us one of the most dangerous nations in the world."Saying, "The only way to stop this madness is to expose the truth                                            \\
 Fake news                                           & Fake news!""When the New York Yankees sent out a message that they did not want them to call themselves a team," Cuomo said of the Yankees' decision to send out this tweet after seeing how much backlash they got from fans."They                                               \\
 Fake news                                           & Fake news \_\_\_\_\_\_\_\_\_\_\_\_, is the only place on the planet people can be sure of knowing what is going on. It is time they spoke about their facts, not those of the political media.\#"It's not just about me though.                                                                \\
 Fake news                                           & Fake news?"I'll be the first to admit it, but I'm not going to go all out on the pro-life president. He has absolutely no idea what the pro-life movement is doing in politics, and I strongly disagree with                                                                      \\
 Voters do not have the ability to                   & Voters do not have the ability to \_\_\_\_\_ to decide for themselves, it seems.""We Are Going To Save Your Life: Donald Trump and Hillary Clinton""The American people were tired and angry on Election Day! President Clinton will not be                                            \\
 Voters do not have the ability to                   & Voters do not have the ability to \_\_\_\_\_ call someone in need of medical attention if they do not respond quickly.". The Huffington Post first reported this:On Tuesday night, a group of students rallied against the Trump administration on Reddit.At this                      \\
 Voters do not have the ability to                   & Voters do not have the ability to \_\_\_\_ the elected official of each state or party, but rather vote to preserve the constitutional validity of our Constitution by voting 'no'. A \#NoNoBorders plan would remove restrictions on marijuana usage." -                              \\
 Democrats want the voters to                        & Democrats want the voters to!!!! That is why I would encourage those who disagree with the way President Trump is treating women!" \#CynthiaNC"If I Were To Become President Donald Trump, Would I Say This Is An Unconstitutional Republic?                                       \\
 Democrats want the voters to                        & Democrats want the voters to \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ for their leadership.""Honeymoon for Donald Trump: Let's see the final day after his election."""""Obama: It's time to build a wall, not a wall. ""                                                                                  \\
 Democrats want the voters to                        & Democrats want the voters to \_\_\_\_\_\_\_\_\_\_\_\_ for a president!""In the wake of the mass shooting in Las Vegas, Republicans on Capitol Hill are saying Democrats need to support the reauthorization of ObamaCare as soon as possible."This isn't a                                    \\
\hline
\end{tabular}