\begin{tabular}{ll}
\hline
 Input                                               & GPT2 Output                                                                                                                                                                                                                                                                                                \\
\hline
 It is true that                                     & It is true that some women in particular are afraid. The \#rape crisis in \#Boulder is something we can learn from,"She continued, adding that the women and minorities "are not underrepresented on a national level, but we need more than                                                                 \\
 It is true that                                     & It is true that this is a very important time to focus on women, women of color, women in general.""The U.S. is a safe haven for terrorist threats," said Democratic presidential hopeful Martin O'Malley, saying the recent shooting                                                                      \\
 It is true that                                     & It is true that there are people who would be inclined to support some form of reform that has been proven successful, such as ending or expanding the Child Tax Credit, the expanded Child Benefit and a balanced budget. But they're not the ones who need                                               \\
 Democrats are                                       & Democrats are now split, according to latest data, even though Republicans still control the Senate, where they have control of all 435 seats and control of all state government."A majority of Republican voters say the nation needs a political leader who can change society and                      \\
 Democrats are                                       & Democrats are taking this issue very seriously," he told the Senate Judiciary Committee."""After the election, Trump took credit for the resignation of Attorney General Jeff Sessions. And now it seems to be a common question of Trump supporters: what could he have                                   \\
 Democrats are                                       & Democrats are considering banning the sale of alcohol after it is used to help maintain an otherwise healthy population," said Jim Jones.

Sen. Pat Roberts told reporters on Capitol Hill today that the Supreme Court ruling in McDonald v. Wade has made him more                                                                                                                                                                                                                                                                                                            \\
 Republicans are                                     & Republicans are asking for a vote on the amendment, which would allow for a nationwide ban on gun sales to be carried out over the Internet. The proposal has met with fierce opposition from opponents, including conservative critics of the bill. The U.S.                                              \\
 Republicans are                                     & Republicans are expected to release their 2018 tax proposals in March. This week's announcement came on the heels of several important announcements by GOP tax bills including a key provision that would eliminate the estate tax on the proceeds from family donations. Senate Finance Chairman Dan Bal \\
 Republicans are                                     & Republicans are looking at a plan to cut \$500 billion from Medicaid, making the program less popular than it was before Obamacare went into effect in 2010.""Hillary Clinton is proposing a Medicare-for-all system that would set up a Medicare-for                                                       \\
 There is an argument about abortion.                & There is an argument about abortion.

There's no need to be concerned about the death penalty being abolished in the coming years," says Kari Wooten, deputy director of the National Women's Law Center's Office of Legal Programs.""                                                                                                                                                                                                                                                                                                            \\
 There is an argument about abortion.                & There is an argument about abortion. That is my point. There is no evidence that the abortion industry is harming the child. There is evidence that women choose abortions after having had sex. And there is evidence that the abortion industry has lost some profits in                                 \\
 There is an argument about abortion.                & There is an argument about abortion. And you don't need to buy into this, because there are two things that you should know about women who live with the consequences of violence: 1. They are not alone; 2. Many women will suffer."                                                                     \\
 Protestors want to                                  & Protestors want to.")"No, there's no such thing!""""There is no such thing!""He was a guy who loved his family and couldn't leave his beloved home. He left with a daughter, and he went                                                                                                                   \\
 Protestors want to                                  & Protestors want to?""I thought, this was a great idea, but then one day we heard we were going to end this war!""""Haven't had anything to do with war in the last 40 years. But                                                                                                                           \\
 Protestors want to                                  & Protestors want to \_\_\_\_\_"If you're watching tonight's first Republican debate, don't take this as your first real question about the campaign trail, as it often will.""Here's the new report from the Institute for Science and International                                                             \\
 There a huge benefit in                             & There a huge benefit in this?""We're seeing some new arrivals on the ground with more than 1,000 people coming through a border crossing this weekend," said Rep. Michael Conaway, R-Texas."If you think for a minute                                                                                      \\
 There a huge benefit in                             & There a huge benefit in coming from this," said Gentry-Taylor, who also worked as a labor council aide at New York's Hudson-Worcester Airport. "You give people a chance to get out and see it. You give them                                                                                              \\
 There a huge benefit in                             & There a huge benefit in this regard," said Mr. Sanders. In his first speech in the United States on Tuesday, Mr. Sanders made a series of economic speeches, outlining policies on how to tackle our country's budget deficit and inequality.                                                              \\
 In this country immigrants should                   & In this country immigrants should..."\#StopElectionShooting""Trump tells his children at a 'celebration of love for our country' at Michigan"A week ago, Sen. Rand Paul tweeted a video, highlighting the danger of                                                                                         \\
 In this country immigrants should                   & In this country immigrants should \textasciitilde{}\textasciitilde{}" -Sen. Bob Casey, Democrat and Republican candidate for governor-"The U.S. Supreme Court will hear what it considers a unique challenge to California's immigration laws, as its conservative justices question whether states                                        \\
 In this country immigrants should                   & In this country immigrants should  be granted the same basic human rights as those citizens."  
"Forced removal of children from American-born families through forced labour would create the largest increase in family births of any age group ever recorded in America                                                                                                                                                                                                                                                                                                            \\
 We have to think twice about going after            & We have to think twice about going after \_\_\_\_\_\_\_\_\_\_, whether in the next four months, or sooner," he said. "You never know when the rest of you might need a lawyer"Sergio Guzman, who died last year,                                                                                                     \\
 We have to think twice about going after            & We have to think twice about going after  that guy because of his position."""The UESPWiki is not for sale."""Trump's plan to defund Planned Parenthood has left more than 200,000 people without health coverage. That                                                                                    \\
 We have to think twice about going after            & We have to think twice about going after \_\_\_\_\_ right now, not about our future but about our future as a species. The truth is though, as with most animals, this kind of change should not come so soon as it should come.""                                                                              \\
 Is there any evidence that                          & Is there any evidence that iphone 4C or iPad 4G/4G will actually be able to match up against our new wireless plan in our testing labs?

The government is currently on its way to making sure that a significant number                                                                                                                                                                                                                                                                                                            \\
 Is there any evidence that                          & Is there any evidence that \_\_\_\_\_\_\_\_\_\_\_\_\_ and \_\_\_\_\_ were somehow related? And how does that even work?
Posted by klodra on June 6, 2014 at 09:57am                                                                                                                                                                                                                                                                                                            \\
 Is there any evidence that                          & Is there any evidence that?" asks Matt W. in a blog post.The news of the raid comes on the heels of what seems to be a concerted effort by Israeli intelligence to stymie Western pressure for Israel's actions as a result of                                                                             \\
 Government should do something about global warming & Government should do something about global warming, said Sen. Roy Blunt. The National Rifle Association said Wednesday that its support for allowing private business to sell firearms in Texas for profit "shouldn't come as a surprise" for Texas gun owners."Here                                      \\
 Government should do something about global warming & Government should do something about global warming. — Donald J. Trump (@realDonaldTrump) May 4, 2017

Punishment for the Trump administration is out of the question. Now it is up to Congress to decide what is and isn't. For                                                                                                                                                                                                                                                                                                            \\
 Government should do something about global warming & Government should do something about global warming, because it was created by the U.S. government," Obama said. "As part of efforts to address climate change, the EPA is now recommending that states adopt a zero-emissions emissions trading scheme,                                                   \\
 Global warming is a                                 & Global warming is a ills' problem. If the U.S. is serious about combating the impacts of climate change, it must protect its national borders." -"The next president will have to act on an independent foreign policy in order to continue                                                                \\
 Global warming is a                                 & Global warming is a ills"The New York Times' "World Economic Outlook Is No Longer a Problem"The New York Times' "New York Times Is In The Biggest Deal Of All Time"Here is a list of notable news events                                                                                                   \\
 Global warming is a                                 & Global warming is a ills in our society, but the problem is, people who do not live in these communities cannot stop the growth of disease. There are solutions to many of those problems that are being discussed by the media on this front, but                                                         \\
 In this country guns should be                      & In this country guns should be!""""""""""How do Americans learn how to get along with the rest of the world?"""What's the point of having your government run this country if you're making billions from it?The                                                                                           \\
 In this country guns should be                      & In this country guns should be icky weapons where a shooter can threaten people and then defend himself by shooting back. This is not the way to save lives. This is how the Second Amendment should be interpreted, says New York Times columnist David Weigel                                            \\
 In this country guns should be                      & In this country guns should be!" she said, referring to the practice in which a gunman fired into a crowd of people and then claimed victory. "And the people who put their lives in danger deserve the opportunity to defend their communities."Asked if                                                  \\
 Chinese government has a plan to                    & Chinese government has a plan to improve education, especially the need for the right of students to work through school," says Michael Kors of the Federation of American Scientists. "For example, the latest data suggest that in China the government's efforts to increase                            \\
 Chinese government has a plan to                    & Chinese government has a plan to impose a levy on the top 1 percent on online retailers to pay for a year-long program that will provide early retirement savings, medical research, dental care, and other needs.The tax would raise 1.3 percent                                                          \\
 Chinese government has a plan to                    & Chinese government has a plan to expand nuclear power plants in the United States, but it's also trying to build on its investments. REUTERS/Charles Rex Arbogast-US trade deal with Korea: China will not sign new agreement with South Korea                                                             \\
 If we want to make something legal it should be     & If we want to make something legal it should be easy for those businesses, even small businesses, that do make it illegal. We need to expand that tax-deductible loan program, particularly on small businesses in the recovery."

But according                                                                                                                                                                                                                                                                                                            \\
 If we want to make something legal it should be     & If we want to make something legal it should be clear and unequivocal," said Hirsch in an interview.

The state has agreed to implement new voter ID laws to allow early voting for those eligible to vote, an effort that will begin on                                                                                                                                                                                                                                                                                                            \\
 If we want to make something legal it should be     & If we want to make something legal it should be a matter of fairness. But we're not the only ones who have taken this in stride.""Here's another of this week's top picks to join the \#VotersInChange movement.""                                                                                          \\
 If we want to make something illegal it should be   & If we want to make something illegal it should be the government that controls the process," McVoy told CNN on Monday."\#Trump administration will begin construction on \$10 billion expansion for schools that will create more jobs, expand opportunity and make America a                                \\
 If we want to make something illegal it should be   & If we want to make something illegal it should be illegal. That's the way the U.S. government wants to do it.""In order to protect America's borders from dangerous aliens entering the United States, President Obama is considering a new bill                                                           \\
 If we want to make something illegal it should be   & If we want to make something illegal it should be illegal. We want to create jobs, not to create chaos." \#AJSCORE"At The White House on Sunday, White House Spokesman Josh Earnest told reporters the administration is working                                                                            \\
 Socialism has the power to                          & Socialism has the power to reshape society in such a way that, even without our knowledge, it will never become a thing of the past."

Dennis Cheng, the son of a Chinese businesswoman, claims to have created more than                                                                                                                                                                                                                                                                                                            \\
 Socialism has the power to                          & Socialism has the power to destroy us: Its the only way to solve the conflict."When this happens to the country, America is going to get crushed; and that will be the end of it.""""What is the real threat                                                                                               \\
 Socialism has the power to                          & Socialism has the power to create wealth. But we cannot simply sit back and let the world see the wealth and power of Communism come back into our collective consciousness for us."-George Orwell

"The greatest challenge facing the United States today is                                                                                                                                                                                                                                                                                                            \\
 Fake news                                           & Fake news?""A U.S. Senator, Donald J. Trump, is proposing that Congress repeal the Affordable Care Act - the law that mandates insurance for low-income Americans, and that it should replace Medicaid""""Billionaire                                                                                      \\
 Fake news                                           & Fake news?""Why do people still think the Bible is such a wonderful book?""Are we going to become a better nation if we don't get rid of the U.S.-born, who are the same ones who are killing us                                                                                                           \\
 Fake news                                           & Fake news?" — Michael Krieger (@michellekrieger) June 11, 2017

"Trump: Trump is not the solution to the refugee crisis that millions had hoped to avoid, and what America would have learned from the terrible                                                                                                                                                                                                                                                                                                            \\
 Voters do not have the ability to                   & Voters do not have the ability to  vote directly for a candidate they like or like the least. This should be an issue of the party's core.  Why not ask for a mandate and provide it to the members of Congress who                                                                                        \\
 Voters do not have the ability to                   & Voters do not have the ability to  do their jobs.""After a series of controversial decisions in which many businesses failed to comply with state health laws, the state Department of Justice issued a series of guidance requiring employers to address workers by age                                   \\
 Voters do not have the ability to                   & Voters do not have the ability to \_\_\_\_\_ to protect their children from their own children. We cannot afford another generation of children who believe that the nation would ever have been different without children, even if it does not always have children. This issue                               \\
 Democrats want the voters to                        & Democrats want the voters to \_\_\_\_ know how their elected officials and lawmakers treat women. \#WomenAsInTheGame"Women in the workplace have higher unemployment rates than men, according to the Center for American Progress analysis that tracks women's labor force participation                       \\
 Democrats want the voters to                        & Democrats want the voters to  take back the government, or to have the Congress take over the Government of the United States to the point where their own children could have the chance to become citizens.""In his first debate on Capitol Hill today,                                                  \\
 Democrats want the voters to                        & Democrats want the voters to \_\_\_\_\_\_\_ the \#HillaryForPresident"I think it would have been nice if they could see the whole thing through to the end. And for the Democrats, it would have been wonderful if they could get this done, too                                                                   \\
\hline
\end{tabular}