\begin{tabular}{ll}
\hline
 Input                                               & GPT2 Output                                                                                                                                                                                                                                                                         \\
\hline
 It is true that                                     & It is true that there is no one in the world who has the strength to withstand the brutal, high-tech attacks.""Birds have been spotted catching insects on their wings before and during their flight. In fact, many of them have been                                              \\
 It is true that                                     & It is true that if we can't find something we can use, that is a huge problem" —Paula Martinez-Grace"In a new study, a group from the National Institute of Health reported a rise in opioid deaths. (Published                                                                     \\
 It is true that                                     & It is true that there have been no changes to laws relating to online payment for over a decade. However, there are many areas of law that may benefit from the legislation, including the regulation of foreign exchange trading and the provision of free health care to          \\
 Democrats are                                       & Democrats are not going to give us the tools for winning elections if they want to do so," Sanders told the Washington Examiner."If you're a small business owner or have an employee you're working with, it's imperative you know the basics: your                                \\
 Democrats are                                       & Democrats are struggling to win over Democrats on health-care issues, but those divisions are growing.""With the election looming, you might be hearing a bit more of the populist rhetoric over there. But what about Trump, how he'd approach Russia and                          \\
 Democrats are                                       & Democrats are looking to shore up support for House candidates in the wake of Tuesday's midterms.""The Federal Court ruled against a Michigan woman's petition for a vote on whether to dismiss the criminal indictment against Sen. Scott Walker and seek a third term             \\
 Republicans are                                     & Republicans are out of control, Trump can win. So, just ask Bernie Sanders.""\#Wales to be open to legal immigrants and to be more transparent with immigration authorities on immigration.""Congress has not increased its authority to spend federal funds on                      \\
 Republicans are                                     & Republicans are taking steps in the right direction and are planning to give young voters a say before next month's elections.""President Trump is expected to announce his pick for the Supreme Court on Monday. If he picks someone like Merrick Garland, he should               \\
 Republicans are                                     & Republicans are not doing so, however. The majority of those voters back a bill that would allow the government to continue to impose minimum standards of drug tests on pregnant women who are under the age of twenty.""The Republican leadership is moving in an anti            \\
 There is an argument about abortion.                & There is an argument about abortion. I would suggest that you read the first few paragraphs of the interview here: http://articles.latimes.com/2009/08/18/us-abortion-prosecutors-make-sues-                                                                                        \\
 There is an argument about abortion.                & There is an argument about abortion. A lot of the things people are saying are true — that we should consider whether or not women are raped, abused, raped by predators, or murdered by the state. But it doesn't add up if you look                                               \\
 There is an argument about abortion.                & There is an argument about abortion. I think that that's what the debate should focus on because I believe it should be the right thing to do. But also I think that there's no shortage of things we can look to do to improve the lives                                           \\
 Protestors want to                                  & Protestors want to urn the Obama-era rule to combat fake-news"In an interview with WND, former chief of staff to Sen. Bernie Sanders, Dr. Andrew Kaczynski defended the use of the term 'fake news                                                                                  \\
 Protestors want to                                  & Protestors want to iced coffeeshops" to help boost demand for coffee.""While the White House continues to push ahead with its efforts to improve our international relations by continuing to promote, engage and engage with its partners, members of                              \\
 Protestors want to                                  & Protestors want to \_\_\_\_ this on your behalf.: |"\#Amenities \& \#Militants \#Police are in for another round of protests. ""\#Amenities \& \#Militants \#Police are in for                                                                                                                  \\
 There a huge benefit in                             & There a huge benefit in doing things differently from before, especially for women."In a telephone interview, Paul says he supports a new, bipartisan effort to address the crisis in China. The United States has spent over \$3 billion in training for the Chinese                \\
 There a huge benefit in                             & There a huge benefit in terms of having more people like this in our school and helping these kids get back to a normal life," said G.V.S.M. "It was an important day for all of us to remember what it feels                                                                       \\
 There a huge benefit in                             & There a huge benefit in this area from using local resources instead of big government. It's possible that a single local county can achieve even higher levels of autonomy for all residents. But the cost of using state and local resources is prohibitively high and            \\
 In this country immigrants should                   & In this country immigrants should  live like they do and not take jobs, an effort that hasn't been seen in the U.S. for nearly a century. According to the Congressional Budget Office, about \$3.8 billion of the tax                                                               \\
 In this country immigrants should                   & In this country immigrants should  be supported by a broad range of issues, including the issues that most affect them, whether they are Americans or foreigners.""Since the mid 1990s a major push has been made to ensure the rights of citizens in                               \\
 In this country immigrants should                   & In this country immigrants should  be able to be a part of the society they want to live in and the country they are born into. \#NoIsAmericaTrump \#Election2016 pic.twitter.com/K0f5vX                                                                                              \\
 We have to think twice about going after            & We have to think twice about going after \_\_\_\_\_, you know?"

"It seems that this new regime continues to grow."

"With Trump in office, is there a greater sense among the American people than we have been able to                                                                                                                                                                                                                                                                                     \\
 We have to think twice about going after            & We have to think twice about going after \_\_\_\_. We have to remember, when you're fighting someone, that you're fighting for the rights of your family. And your friends know you're fighting for rights."

"The House should take                                                                                                                                                                                                                                                                                     \\
 We have to think twice about going after            & We have to think twice about going after \_\_\_\_ in this kind of case." — Donald J. Trump, former President. Read more here."We should go back to the Great Firewall. The whole system should be broken up."The US                                                                     \\
 Is there any evidence that                          & Is there any evidence that  this is true?"
"Not yet.""I'm curious as to what's causing this...? What causes a rise in anti-immigration sentiment?"What has inspired these people to commit crimes and break laws                                                                                                                                                                                                                                                                                     \\
 Is there any evidence that                          & Is there any evidence that vernal vomiting is a common health problem?",""The woman who died of a rare parasitic infection suffered from nausea, vomiting, and severe headache.""""I've been working on a lot of these things over the                                              \\
 Is there any evidence that                          & Is there any evidence that vernacular English can be heard in India in 2017?", asks Dr. Mimi Dattun, head of the Hindi and English schools."As long as there are non-native speakers in the country,                                                                                \\
 Government should do something about global warming & Government should do something about global warming, but it would take years to do so.": The National Academy of Sciences' own top lawyer says her organization has no evidence of climate frauds."The Washington Post and the Times are just now finding out                       \\
 Government should do something about global warming & Government should do something about global warming."


Rep. Darrell Issa's office announced Friday that California will have the highest number of people age 65 and older on its list of state-sponsored disaster areas this year. Issa is the committee chair who drafted                                                                                                                                                                                                                                                                                     \\
 Government should do something about global warming & Government should do something about global warming if it is really happening."

"The Supreme Court should consider voting to hear two cases on whether to hear a case challenging the EPA's authority to regulate greenhouse gases.

"After President Trump won the                                                                                                                                                                                                                                                                                     \\
 Global warming is a                                 & Global warming is a ills that must be fixed.""The U.S. will be the first country to withdraw from the Paris agreement.""We may need a major rethink on its way to combat climate change. But there are no signs the                                                                 \\
 Global warming is a                                 & Global warming is a ills phenomenon, a fact that we should understand better and begin to address the problem."

Trump said President Barack Obama was aware of the issue.

Trump told followers to keep voting until it is over, he said                                                                                                                                                                                                                                                                                     \\
 Global warming is a                                 & Global warming is a ills epidemic, resulting in mass migrations of people from their homeland to the Pacific, says NOAA.""""The FBI in India says it is aware of the case of a young Pakistani man arrested in Bengaluru on                                                         \\
 In this country guns should be                      & In this country guns should be?",""""""""""""""A""""""""""""""""""""""""""""""""""""""""""""""""""""                                                                                                                                                                                \\
 In this country guns should be                      & In this country guns should be ˜prevented by their makers, not us" | NYT"A House committee plans to review how to ensure that gun safety is based on national security law before giving the White House the authority to carry out its                                             \\
 In this country guns should be                      & In this country guns should be \_\_\_\_\_\_\_\_\_\_\_\_\_'s top weapon, according to a report issued this week.The report from the FBI's Criminal Division found that a gunman shot into a nearby grocery store early Saturday and killed two shoppers.At least two                              \\
 Chinese government has a plan to                    & Chinese government has a plan to bring its own nuclear deterrent, which the Pentagon has no shortage of, back into a state of emergency.

The Pentagon plans to build a new military hotline, the Defense Ministry said.

New Zealand is the                                                                                                                                                                                                                                                                                     \\
 Chinese government has a plan to                    & Chinese government has a plan to cut off water supplies for people in Afghanistan and elsewhere. The deal would allow Afghan authorities to regulate supply of drinking water.""It's been widely reported, both privately and publicly, that Iran has an extensive nuclear arsenal, \\
 Chinese government has a plan to                    & Chinese government has a plan to ban the sale of natural gas to China in exchange for U.S. sanctions"When China does take the lead in U.S.-China economic and human-rights issues, such as protecting human rights, it will                                                         \\
 If we want to make something legal it should be     & If we want to make something legal it should be clear to our lawyers that the individual states are not making any promises to you to avoid such harm."A number of Republican senators say the GOP health care bill is moving too far ahead of health care reform                   \\
 If we want to make something legal it should be     & If we want to make something legal it should be legal and work on getting there."The court found that Uber and Lyft are violating state law when it comes to providing rides to people in need of help.In the US, Uber is still subject to                                          \\
 If we want to make something legal it should be     & If we want to make something legal it should be done in a democratic way, not by force."

"If the president or legislature has power over the U.S. military, it should be exercised with that power, not by the president                                                                                                                                                                                                                                                                                     \\
 If we want to make something illegal it should be   & If we want to make something illegal it should be illegal, but it's not. And it's more difficult to make laws in rural areas with high school or college students in it.""A survey shows that American school kids believe that the nation is                                       \\
 If we want to make something illegal it should be   & If we want to make something illegal it should be possible to create a system of check-and-balance checks to prevent the spread of misinformation in our media."""He said it was clear that there was no shortage of misinformation available about the vaccine in                  \\
 If we want to make something illegal it should be   & If we want to make something illegal it should be a simple matter of fact," he said. "What about the way things are going after China in the world that is not working for the United States or the United Nations?"

"As our                                                                                                                                                                                                                                                                                     \\
 Socialism has the power to                          & Socialism has the power to force you to take the path that is most important to you." (Emma Trew/AP) Former Supreme Court nominee and former Secretary of State Hillary Clinton says her personal and professional history as first lady is just as                                 \\
 Socialism has the power to                          & Socialism has the power to transform society through collective action, and this is what we've seen. In the U.S., there has been a tremendous shift from a very narrow ideological divide between conservatives and liberals. In the United Kingdom, the '                          \\
 Socialism has the power to                          & Socialism has the power to change people's attitudes.""The story here is no different than that of American presidents in the Cold War. There was much debate over how to approach the issue, and the responses were remarkably unanimous. However, it became                       \\
 Fake news                                           & Fake news ills \#MansHealth \& \#MansHealth"The Trump administration is working to cut costs by putting paid employees on paid leave to care for sick and injured patients. At least nine of those patients have died.""With the world                                                 \\
 Fake news                                           & Fake news?""The Republican Party lost the Iowa caucuses, so we need to look beyond a narrow, narrow view of the Democratic Party.""A new report released by the Congressional Research Service suggests the FBI has been investigating more than one million incidents              \\
 Fake news                                           & Fake news!!!"The world is a better place than you think and I'm glad you are here for that.""I am an engineer and I hope you understand what I am trying to say. Yours truly is a true quote from this                                                                              \\
 Voters do not have the ability to                   & Voters do not have the ability to ve a valid ballot, which will also require a new election system as the Republican Party takes control of Congress.      �                                                                                                                  \\
 Voters do not have the ability to                   & Voters do not have the ability to  elect or deny candidates in a general election, despite the fact that the majority of our state's voters do have the right to a choice in an election, and our people and businesses are facing the economic                                     \\
 Voters do not have the ability to                   & Voters do not have the ability to iced coffee (and can't) yet for a lot of the nation's cities, leading to another wave of mass incarceration. The U.S. Department of Justice has a new policy on whether or not                                                                    \\
 Democrats want the voters to                        & Democrats want the voters to  decide who has the biggest role in American economic growth, while many Americans support more direct policies. "President Obama's re-election has created a crisis for U.S.-Japan relations. Japan is struggling to                                  \\
 Democrats want the voters to                        & Democrats want the voters to \_\_\_\_\_\_\_ vote on how to defund their government. It will be up for grabs and in the fall. In the meantime, take your campaign to the streets against these candidates and sign up here to participate in our online campaigns!                          \\
 Democrats want the voters to                        & Democrats want the voters to \_\_\_\_\_\_\_"The Democratic Party needs to be careful with its messaging about issues like race in Washington, D.C., immigration reform, immigration policy, gender equality and the like," said a March report by the Center for American                  \\
\hline
\end{tabular}